Out-of-Sample Comparisons of Overfit Models

### 2014-03-21 paper.tex
Empirics: clean up table listing Goyal and Welch variables
This commit adds the booktabs and tabularx packages to the
preamble and moves the list of Goyal Welch variables to
a booktabs table.

The first table was smushed into the bibliography; that's been fixed
now and it's on its own page.

\bibliographystyle{abbrvnat}
\bibliography{references}

\begin{table}[h]
 \begin{multicols}{2}
  \begin{itemize}
  \item log Dividend Price Ratio
  \item log Earnings Price Ratio
  \item Stock Market Variance
  \item Book to Market Ratio
  \item Net Equity Expansion
  \item Percent Equity Issuing
  \item Treasury Bill
  \item Long Term Yield
  \item Long Term Rate
  \item Default Return Spread
  \item Default Yield Spread
  \item Inflation
  \end{itemize}
 \end{multicols}
 \caption{Variables used in Section \ref{sec:empirics} and by Goyal
   and Welch (2008) to predict the equity premium.  Please see Goyal
   and Welch's original paper
   for a detailed description of each variable.}
 \label{tab:equity}
\end{table}

>>>>

\bibliographystyle{abbrvnat}
\bibliography{references}
\clearpage

\begin{table}[tb]
  \begin{tabularx}{\linewidth}{XX}
    \toprule
    Category & Variable \\
    \midrule
    Stock market variables
    & Dividend Price ratio (log) \\
    & Earnings Price ratio (log) \\
    & Stock Market Variance \\
    & Book to Market Ratio \\
    & Net Equity Expansion \\
    & Percent Equity Issuing \\\\
    Interest rate variables
    & Treasury Bill rate (3 month) \\
    & Long Term Yield \\
    & Long Term Rate \\
    & Default Return Spread \\
    & Default Yield Spread \\
    & Inflation \\
    \bottomrule
  \end{tabularx}
  \caption{Variables used to predict the equity premium.
    Please see Goyal and Welch's original paper \citep{GoW:08}
    for a detailed description of each variable.}
  \label{tab:equity}
\end{table}
